---
title: "CoV-19 Community Data Summary"
date: "Today"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<<<<<<< HEAD
```{r "Load scripts", include=FALSE}
source("Constants and dependencies.R")
source("Functions.R")
```
```{r "Load FIPS data sets", message=TRUE, include=FALSE}

USA_FIPS_data <- read_csv(file = "data/VHA_FIPS_20170920.csv") %>%
  select(State, County, FIPS, VISN, Market = `Market Description`, Network = `VISN Description`) %>%
  mutate(Market = str_remove(Market, "^.{4}"))  %>% # Remove the first 4 characters
  mutate(Market = str_replace_all(Market, "_", " ")) %>%
  mutate(Network = str_remove(Network, "^VA "))  %>% # Drop leading "VA "
  mutate(State = str_to_title(State)) %>%
  mutate(State =ifelse(grepl(paste(non_state, collapse = "|"), State), NA, State)) %>%  # Drop non-states. The paste() function creates a RegEx of values separated by '|'.
  drop_na()

```

```{r "Load JHU data sets" message=FALSE, include=FALSE}
USA_cases_all <- import_JHU_data()
county_VHA_COVID_data <- USA_cases_all %>%
  select(-State, -County) %>%
  filter(Cases > 0) %>%
  group_by(FIPS) %>%
  arrange(Date) %>%
  mutate(Recovered = lag(Alive, recovery_time)) %>% #Returns NA for days 1-recovery_time
  replace_na(list(Recovered = 0)) %>% # Replaces NAs with zero
  mutate(Active = Alive - Recovered) %>%
  filter (Active >= 0) %>% # Remove errors from bad data
  right_join(y = USA_FIPS_data, by = "FIPS")
```

```{r eval=FALSE, include=FALSE}
rm(list = c("packages",
            "US_cases_confirmed_URL",
            "US_cases_deceased_URL",
            "non_state"
            )
   )
```


=======
```{r "Source files", include=FALSE}
source("Constants and dependencies.R")
source("Functions.R")
```
```{r, include=FALSE}
USA_cases_all <- import_JHU_data()

USA_FIPS_data <- read_csv(file = "data/VHA_FIPS_20170920.csv") %>%
  select(State, County, FIPS, VISN, Market)
```

>>>>>>> d78d48cdc4dff345899c66b9031c15d858d49f52
